\textbf{Adaptation of the PHQ-4 Short Screening for Depression and Anxiety to increase its Sensitivity to Subclinical Variability}

### 2023-01-08 paper/manuscript.Rmd
fix

The reliability of the anxiety ($Cronbach's~\alpha = 0.903$; RMSEA = 0.031) and depression ($Cronbach's~\alpha = 0.841$; RMSEA = 0.044) subscales is excellent. The proportion of response types stratified by item (see **Figure 1A**) shows that the new "Once or twice" option was the most prevalent response for all items (on average selected in **29.12\%** of cases).

@@

Item Response Theory (IRT) provides insights into how well items and responses capture an underlying latent trait $\theta$. For each of the subscales, we fitted a unidimensional graded response model [GRM, @samejima1997graded]. For anxiety, the two items captured 89.2\% of the variance of the latent anxiety dimension ($\theta_{anxiety}$). The discrimination parameters suggested that the first item was less precise ($\alpha = 3.42$) than the second item ($\alpha = 12.55$) in its ability to discriminate between various levels of anxiety (i.e., each response on item 1 covers a more exclusive range of $\theta_{anxiety}$, as can be seen in **Figure 1B**). The two depression items captured 82.8\% of the variance of its latent trait ($\theta_{depression}$), and the opposite pattern was found: the first item had a higher precision ($\alpha = 16.46$) than the first ($\alpha = 2.41$). However, it is important to note that the "less precise" items were also the ones covering a larger portion of the latent space (being more sensitive on the lower end of the spectrum), offering an interesting trade-off between sensitivity and precision. Importantly, for our objective, it seems that the added "Once or twice" option does cover a selective and unique portion of the latent space.

>>>>

The reliability of the anxiety ($Cronbach's~\alpha = 0.903$; RMSEA = 0.031) and depression ($Cronbach's~\alpha = 0.841$; RMSEA = 0.044) subscales is excellent. The proportion of response types stratified by item (see **Figure 1A**) shows that the new "Once or twice" option was the most prevalent response for all items (on average selected in 29.12\% of cases).

@@

Item Response Theory (IRT) provides insights into how well items and responses capture an underlying latent trait $\theta$. For each of the subscales, we fitted a unidimensional graded response model [GRM, @samejima1997graded]. For anxiety, the two items captured 89.2\% of the variance of the latent anxiety dimension ($\theta_{anxiety}$). The discrimination parameters suggested that the first item was less precise ($\alpha = 3.42$) than the second item ($\alpha = 12.55$) in its ability to discriminate between various levels of anxiety (i.e., each response on the second item covers a more exclusive range of $\theta_{anxiety}$, as can be seen in **Figure 1B**). The two depression items captured 82.8\% of the variance of its latent trait ($\theta_{depression}$), and the opposite pattern was found: the first item had a higher precision ($\alpha = 16.46$) than the first ($\alpha = 2.41$). However, it is important to note that the "less precise" items were also the ones covering a larger portion of the latent space (being more sensitive especially on the lower end of the spectrum), offering an interesting trade-off between sensitivity and precision. Importantly for our objective, the added "Once or twice" option does cover a selective and unique portion of the latent space.

### 2023-01-08 paper/manuscript.tex
fix

The reliability of the anxiety (\(Cronbach's~\alpha = 0.903\); RMSEA = 0.031) and depression (\(Cronbach's~\alpha = 0.841\); RMSEA = 0.044) subscales is excellent. The proportion of response types stratified by item (see \textbf{Figure 1A}) shows that the new ``Once or twice'' option was the most prevalent response for all items (on average selected in \textbf{29.12\%} of cases).

@@

Item Response Theory (IRT) provides insights into how well items and responses capture an underlying latent trait \(\theta\). For each of the subscales, we fitted a unidimensional graded response model (GRM, Samejima, 1997). For anxiety, the two items captured 89.2\% of the variance of the latent anxiety dimension (\(\theta_{anxiety}\)). The discrimination parameters suggested that the first item was less precise (\(\alpha = 3.42\)) than the second item (\(\alpha = 12.55\)) in its ability to discriminate between various levels of anxiety (i.e., each response on item 1 covers a more exclusive range of \(\theta_{anxiety}\), as can be seen in \textbf{Figure 1B}). The two depression items captured 82.8\% of the variance of its latent trait (\(\theta_{depression}\)), and the opposite pattern was found: the first item had a higher precision (\(\alpha = 16.46\)) than the first (\(\alpha = 2.41\)). However, it is important to note that the ``less precise'' items were also the ones covering a larger portion of the latent space (being more sensitive on the lower end of the spectrum), offering an interesting trade-off between sensitivity and precision. Importantly, for our objective, it seems that the added ``Once or twice'' option does cover a selective and unique portion of the latent space.

>>>>

The reliability of the anxiety (\(Cronbach's~\alpha = 0.903\); RMSEA = 0.031) and depression (\(Cronbach's~\alpha = 0.841\); RMSEA = 0.044) subscales is excellent. The proportion of response types stratified by item (see \textbf{Figure 1A}) shows that the new ``Once or twice'' option was the most prevalent response for all items (on average selected in 29.12\% of cases).

@@

Item Response Theory (IRT) provides insights into how well items and responses capture an underlying latent trait \(\theta\). For each of the subscales, we fitted a unidimensional graded response model (GRM, Samejima, 1997). For anxiety, the two items captured 89.2\% of the variance of the latent anxiety dimension (\(\theta_{anxiety}\)). The discrimination parameters suggested that the first item was less precise (\(\alpha = 3.42\)) than the second item (\(\alpha = 12.55\)) in its ability to discriminate between various levels of anxiety (i.e., each response on the second item covers a more exclusive range of \(\theta_{anxiety}\), as can be seen in \textbf{Figure 1B}). The two depression items captured 82.8\% of the variance of its latent trait (\(\theta_{depression}\)), and the opposite pattern was found: the first item had a higher precision (\(\alpha = 16.46\)) than the first (\(\alpha = 2.41\)). However, it is important to note that the ``less precise'' items were also the ones covering a larger portion of the latent space (being more sensitive especially on the lower end of the spectrum), offering an interesting trade-off between sensitivity and precision. Importantly for our objective, the added ``Once or twice'' option does cover a selective and unique portion of the latent space.
